Notes

### 2020-02-28 Notes/Notes.tex
Typos

\section{Asking MDS Question}
Instead of minimizing the size of the minimum dominating set under constraints, we can also ask if the number of nodes is smaller than an input dominating number
\begin{equation}
	\sum_{i \in V} x_i \leq \gamma_D \quad \Rightarrow \quad \sum_{i \in V} x_i - \gamma_D + s_D = 0 \, .
\end{equation}
Note that we still obtain solution vectors.
In principle this means one has to iterate approaches to get the best energy solution but it is also possible to find $E_0 = \gamma + n$ with $n\geq1$.
The QUBO now becomes
\begin{align}\label{mds2:qubo}
	Q &= 
	\begin{pmatrix}\alpha & \beta & 0 \\ 0 & \gamma & 0 \\ 0 & 0 & 0 \end{pmatrix}
	+
	A \begin{pmatrix}\alpha' & 0 & \beta' \\ 0 & 0 & 0 \\ 0 & 0 & \gamma' \end{pmatrix}
	\, , & 
	f(\vec x, \vec s, s_D)
	&=
	\vec \psi \cdot Q \cdot \vec \psi + |V| + A \gamma_D^2
	\, ,
\end{align}
where $\alpha, \beta, \gamma$ are the same as before and $\alpha', \beta', \gamma'$ implement the new constraint.
In particular 
\begin{align}
	\vec x \cdot \alpha' \vec x &= \left(\sum_i x_i\right)^2 - 2 \left(\sum_i x_i\right) \gamma_D 
	&& \Rightarrow &
	\alpha' &= \vec 1_x \vec 1_x^T - 2 \gamma_D \mathbbm{1}_x
	\\
	\vec x \cdot \beta' \vec s &= 2 \left(\sum_i x_i\right) s_D \gamma_D 
	&& \Rightarrow &
	\beta' &= 2 \gamma_D \vec 1_x B'
	\\
	\vec s \cdot \gamma' \vec s &= s_D^2 - 2 s_D \gamma_D 
	&& \Rightarrow &
	\alpha' &= B'^T B' - 2 \gamma_D B'
	\\
\end{align}

>>>>

\section{Asking MDS Question}
Instead of minimizing the size of the minimum dominating set under constraints, we can also ask if the number of nodes is smaller than an input dominating number
\begin{equation}
	\sum_{i \in V} x_i \leq \gamma_D \quad \Rightarrow \quad \sum_{i \in V} x_i - \gamma_D + s_D = 0 \, .
\end{equation}
This approach is interesting as it is constraints only.
Note that we still obtain solution vectors.
In principle this means one has to iterate approaches to get the best energy solution but it is also possible to find $E_0 = \gamma - n$ with $n\geq1$.
The QUBO now becomes
\begin{align}\label{mds2:qubo}
	Q &= 
	\begin{pmatrix}\alpha & \beta & 0 \\ 0 & \gamma & 0 \\ 0 & 0 & 0 \end{pmatrix}
	+
	A \begin{pmatrix}\alpha' & 0 & \beta' \\ 0 & 0 & 0 \\ 0 & 0 & \gamma' \end{pmatrix}
	\, , & 
	f(\vec x, \vec s, s_D)
	&=
	\vec \psi \cdot Q \cdot \vec \psi + |V| + A \gamma_D^2
	\, ,
\end{align}
where $\alpha, \beta, \gamma$ are the same as before and $\alpha', \beta', \gamma'$ implement the new constraint.
In particular 
\begin{align}
	\vec x \cdot \alpha' \vec x &= \left(\sum_i x_i\right)^2 - 2 \left(\sum_i x_i\right) \gamma_D 
	&& \Rightarrow &
	\alpha' &= \vec 1_x \vec 1_x^T - 2 \gamma_D \mathbbm{1}_x
	\\
	\vec x \cdot \beta' \vec s &= 2 \left(\sum_i x_i\right) s_D \gamma_D 
	&& \Rightarrow &
	\beta' &= 2 \gamma_D \vec 1_x B'
	\\
	\vec s \cdot \gamma' \vec s &= s_D^2 - 2 s_D \gamma_D 
	&& \Rightarrow &
	\alpha' &= B'^T B' - 2 \gamma_D B'
	\\
\end{align}
